%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[11pt, a4paper]{awesome-cv}

%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
%\colorlet{awesome}{awesome-darknight}
\definecolor{awesome}{HTML}{17202A}
%% Colors for text
\definecolor{darktext}{HTML}{17202A}
\definecolor{text}{HTML}{17202A}
\definecolor{graytext}{HTML}{17202A}
\definecolor{lighttext}{HTML}{17202A}


%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     3rd party packages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Needed to divide into several files
\usepackage{import}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Essentials
\name{}{Manju M. Johny}
\address{2414 Snedecor Hall, 2438 Osborn Drive, Ames, IA, 50011}
\mobile{} 
%%% Social
\email{mjohny@iastate.edu}
\homepage{mjohny.github.io}
\github{mjohny}
\linkedin{mjohny}
%%% Optionals
%\position{Software Engineer{\enskip\cdotp\enskip}Security Expert}
%\quote{``Make the change that you want to see in the world."}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Make a footer for CV with three arguments(<left>, <center>, <right>)
\makecvfooter
  {\today}
  {Manju M. Johny~~~·~~~mjohny@iastate.edu}
  {\thepage}

\newenvironment{cventries2}{%
  \vspace{\acvSectionContentTopSkip}
  \begin{center}
}{%
  \end{center}
}



\begin{document}
%%% Make a header for CV with personal data
\makecvheader

%%% Import contents
\cvsection{Education}
\vspace{1mm}
\begin{cventries}
    \cventry
    {Iowa State University}
    {Doctor of Philosophy in Statistics}
    {Ames, IA}
    {Aug. 2014 - May 2020 (Expected)}
    {
 %     \begin{cvitems}
 %       \item {}
 %     \end{cvitems}
    }
  \end{cventries}
  \vspace*{-\baselineskip}
  \begin{cventries}
    \cventry
    {Iowa State University}
    {Master of Science in Statistics}
    {Ames, IA}
    {Aug. 2014 - May 2017 (Expected)}
    {
 %     \begin{cvitems}
 %       \item {}
 %     \end{cvitems}
    }
  \end{cventries}
  \vspace*{-\baselineskip}
  \begin{cventries}
  \cventry
    {Saint Louis University}
    {Bachelor of Arts in Mathematics and Chemistry}
    {St. Louis, MO}
    {Aug. 2010 - May 2014}
    {
 %     \begin{cvitems}
 %       \item {}
 %     \end{cvitems}
    }
\end{cventries}
\vspace*{-\baselineskip}


\cvsection{Skills}

\begin{cvskills}
  \cvskill
    {Programming} % Category
    {R, LaTeX, SAS, JMP, Excel} % Skills
  \cvskill
    {Languages} % Category
    {English (native); Malayalam (native); Spanish (limited working fluency)} % Skills
\end{cvskills} 

\cvsection{Honors \& Awards}
\cvsubsection{International}
\begin{cvhonors}
  \cvhonor
    {Second Place}
    {Prudsys Data Mining Cup}
    {Berlin, Germany}
    {2016}
 \end{cvhonors}

\cvsubsection{Domestic}
\begin{cvhonors}
  \cvhonor
    {Alumni Fellowship}
    {Iowa State University}
    {Ames, IA}
    {2014}
  \cvhonor
    {ORISE Fellowship}
    {Oak Ridge Institute for Science and Education; US FDA}
    {St. Louis, MO}
    {2013-14}
    \cvhonor
    {Pi Mu Epsilon Member}
    {US National Mathematics Honor Society}
    {}
    {2014}
  \cvhonor
    {Dean's List}
    {Saint Louis University}
    {St. Louis, MO}
    {2013}
   \cvhonor
    {Vice President's Scholarship}
    {Saint Louis University}
    {St. Louis, MO}
    {2010-14}
  \cvhonor
    {Bright Flight Scholarship}
    {Missouri Department of Higher Education}
    {St. Louis, MO}
    {2010-14}
  \cvhonor
    {Advanced Placement Scholar with Distinction}
    {The College Board}
    {}
    {2010}
\end{cvhonors}

 \cvsection{Research}
\begin{cventries}
\cventry
    {\textbf{Iowa State University} \newline Mentor: Petrutza Caragea, Ph.D}
    {Master's Creative Component: \newline Assymptotic functional ANOVA for ecological time series data}
    {Ames, IA}
    {2016}
    {
      \begin{cvitems}
        \item Utilized an assymptotic functional ANOVA approach to study treatment effects of heating and snow removal on soil moisture and temperature time series data. Approach involved smoothing data using fourier and b-spline basis, and generating bootstrap resample curves using the covariance structure of the original data.   
        \item Expected date of defense: Spring 2017
      \end{cvitems}
    }
\end{cventries}

\begin{cventries}
  \cventry
    {\textbf{DPA/CDER/US Food and Drug Administration.} \newline Mentors: Jason Rodrigues, Ph.D; Connie Gryniewicz-Ruzicka, Ph.D}
    {Research Fellow}
    {St. Louis, MO}
    {Summer 2014 \newline}
    {
      \begin{cvitems}
        \item {Developed an algorithm in MATLAB to transfer laboratory methods to field instruments}
        \item {Developed rapid screening methods to identify adulteration of pharmaceutical materials on bench top and portable Ion Mobility Spectrometry instruments.}
        \item {Research culminated in a formal talk to Deparmtent of Pharmaceutical Analysis, CDER/FDA.}
      \end{cvitems}
    }
\end{cventries}
\vspace*{-\baselineskip}
\begin{cventries}
  \cventry
    {\textbf{DPA/CDER/US Food and Drug Administration.} \newline Mentors: Jason Rodrigues, Ph.D; Hongping Ye, Ph.D}
    {}
    {}
    {Summer 2013 \newline}
    {
      \begin{cvitems}
        \item {Devoped statistical methods for disaccharide analysis to test for ruminant contanmination in heparin. }
        \item {Developed Raman and near Infrared spectral libraries for screening of pharmaceutical materials.}
        \item {Research culminated in formal talk to Department of Pharmaceutical Analysis, CDER/FDA, and poster presentation at Center for Drug Evaluation and Research Science Day in White Oak, MD.}
      \end{cvitems}
    }
    \end{cventries}
\vspace*{-2\baselineskip}
\cvsection{Teaching}
\cvsubsection{Instructor}
\begin{cvhonors}
  \cvhonor
    {STAT 101: Principles of Statistics}
    {Iowa State University}
    {Ames, IA}
    {2015-16}
 \end{cvhonors}
 \cvsubsection{Lab Instructor}
\begin{cvhonors}
  \cvhonor
    {STAT 101: Principles of Statistics}
    {Iowa State University}
    {Ames, IA}
    {2014-15}
 \end{cvhonors}
  \cvsubsection{Grader}
\begin{cvhonors}
  \cvhonor
    {STAT 104: Introduction to Statistics}
    {Iowa State University}
    {Ames, IA}
    {2014-15}
  \cvhonor
    {STAT 401: Statistical Methods for Research Workers}
    {Iowa State University}
    {Ames, IA}
    {2015}
 \end{cvhonors}
\cvsubsection{Tutor}
  \begin{cvhonors}
  \cvhonor
    {Statistics Tutor}
    {Saint Louis University}
    {St. Louis, MO}
    {2013-14}
  \cvhonor
    {Mathematics Tutor}
    {Jefferson College}
    {Hillsboro, MO}
    {2010}
 \end{cvhonors}
 
\cvsection{Publications}
\small{Rodriguez, J. D.; Skaggs, S.K.; Johny, M.; Srivastiva, H.K.; Loethen, Y.L.; Arzhantsev, S.; Kauffman, J. F.; Buhse, L.F.  Distribution of Spectral Libraries Across Different Field Deployable Raman and Near Infrared Instruments. Am. Pharm. Review 2014, 17, 10-17.}
 
\cvsection{Abstracts \& Presentations}
\cvsubsection{Abstracts}\\
\small{
Jason D. Rodriguez, Steven K. Skaggs, Manju M. Johny, Hirsch K. Srivastava, and Yvette L. Loethen, “Evaluating the Performance of Field Screening Using Portable Raman and Near Infrared Spectrometers” IFPAC Conference; Feb. 2015.
}

\cvsubsection{Presentations}\\
\small{
Manju M. Johny, Steven K. Skaggs, Connie M. Gryniewicz-Ruzicka, Jason D. Rodriguez, “Development of IMS Library for Detection of Adulterants; Standardization of Ramen Spectra Across 5 Different Instruments” FDA Summer Research Symposium, St. Louis, MO USA; Aug 2014.
\\\\ 
Jason D. Rodriguez, Steven K. Skaggs, Manju M. Johny, Sergey Arzhantsev, Yvette L. Loethen, Hirsch K. Srivastava, John F. Kauffman, and Lucinda F. Buhse, "Developing Spectral Libraries for Domestic and Foreign Screening of Pharmaceutical Materials" CDER Science Day; White Oak, MD USA; Sept 2013.
\\\\
Manju M. Johny, Hongping Ye, “Disaccharide Analysis to Test Ruminant Contamination of Heparin” FDA Summer Research Symposium, St. Louis, MO USA; Aug 2013.
}

\cvsection{Activities \& Community Outreach}
  \begin{cvhonors}
  \cvhonor
    {Iowa State STATers}
    {Iowa State University}
    {Ames, IA}
    {2014-16}
  \cvhonor
    {Chemistry Club; Position: Demonstration Captain}
    {Saint Louis University}
    {St. Louis, MO}
    {2012-13}
  \cvhonor
    {Volunteer at Sunrise Assisted Living}
    {}
    {Des Peres, MO}
    {2008-13}
  \cvhonor
    {Lion's Club International; Vision Screening Community}
    {Saint Louis University}
    {St. Louis, MO}
    {2013}
 \end{cvhonors}

\cvsection{Graduate Courses}

STAT 500: Statistical Methods I \dotfill \textit{\small{Fall 2014}}\\
STAT 510: Statistical Methods II \dotfill \textit{\small{Spring 2015}}\\
STAT 520: Statistical Methods III \dotfill \textit{\small{Fall 2015}}\\
STAT 611: Theory \& Application of Linear Models \dotfill \textit{\small{Fall 2016}}\\
STAT 542: Theory of Probability \& Statistics I \dotfill \textit{\small{Fall 2014}}\\
STAT 543: Theory of Probability \& Statistics II \dotfill \textit{\small{Spring 2016}}\\
STAT 641: Foundation of Probability Theory \dotfill \textit{\small{Fall 2016}}\\
STAT 551: Time Series Analysis \dotfill \textit{\small{Fall 2015}}\\
STAT 534: Ecological Statistics \dotfill \textit{\small{Fall 2015}}\\
STAT 544: Bayesian Statistics \dotfill \textit{\small{Spring 2016}}\\
STAT 579: An Introducation to R \dotfill \textit{\small{Fall 2014}}\\
STAT 580: Statistical Computing \dotfill \textit{\small{Spring 2015}}



\end{document}
